openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Add dots to nodes_repos and nodes_users

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph),
                                   edges_common_users(oarch_graph))

@@

```{r plot-graph-user-user}
oarch_graph_user_user <- tbl_graph(nodes_users(oarch_graph), 
                                   edges_common_repos(oarch_graph))

>>>>

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph, category),
                                   edges_common_users(oarch_graph))

@@

```{r plot-graph-user-user}
oarch_graph_user_user <- tbl_graph(nodes_users(oarch_graph, category), 
                                   edges_common_repos(oarch_graph))
